%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
    \cventry
    {Senior Technical Advisor} % Job title
    {Dagozilla Robotics (Autonomous Vehicle Research Group Lab, ITB)} % Organization
    {Bandung, Indonesia} % Location
    {Sept 2019 - Present} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Gives technical advises and feedbacks to the software/programming team.}
            \item {Does more advanced research in state estimation and implementations of Bayesian filters.}
        \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
	{Lead Software Engineer} % Job title
	{} % Organization
	{} % Location
	{Sept 2018 - Sept 2019} % Date(s)
	{
	  \begin{cvitems} % Description(s) of tasks/responsibilities
	  	\item {Led the design and development process of the software system for a telepresence robot as well as the documentation of the system.}
		\item {Directed the research and development on computer vision, robotic control systems, robot AI, and software UI/UX for MSL-class robots.}
		\item {Designed and implemented AI for a MSL-class goalkeeper robot behavior and decision making using ROS as middleware in Python.}
		\item {Implemented algorithm for robot pose estimation by combining odometry and heading sensor data using Monte Carlo Localization.}
		\item {Initiated better engineering and software documentation practices that enable the sharing of knowledge between divisions.}
	  \end{cvitems}
	}

%---------------------------------------------------------
  \cventry
	{Software Engineer} % Job title
	{} % Organization
	{} % Location
	{Sept 2017 - Sept 2018} % Date(s)
	{
	  \begin{cvitems} % Description(s) of tasks/responsibilities
%		\item {Designed architecture for computer vision system software for football-playing robots that compete in MSL-class competitions.}
%		\item {Designed and built a software component for object detection for MSL-class competition robots using OpenCV with ROS in C++.}
		\item {Designed and built the computer vision software component for MSL-class competition robots using OpenCV with ROS in C++.}
		\item {Created software documentation of the vision system that I built as well as other legacy codes that were going to be migrated.}
        \item {Initiated the research on a pose estimation method by combining odometry and IMU sensor data using Extended Kalman Filter.}
	  \end{cvitems}
	}

%---------------------------------------------------------
\cventry
{Software Engineer Intern} % Job title
{Shopee International Indonesia} % Organization
{Jakarta, Indonesia} % Location
{May 2019 - Aug 2019} % Date(s)
{
	\begin{cvitems} % Description(s) of tasks/responsibilities
		\item {Implemented back end handler component that deals with a high number of requests per second in Golang.}
		\item {Created ``Feature Release Manager'' application which allows independent and individual releases of features for different countries in Golang.}
		\item {Wrote software documentation of ``Feature Release Manager'' application and other software components that I implemented.}
	\end{cvitems}
}



\end{cventries}
