%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Organizational Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
\cventry
{Head of Aspiration Committee, Council of Supervisory and Representatives} % Job title
{Computer Science Student Union, ITB} % Organization
{Bandung, Indonesia} % Location
{March 2019 - March 2020} % Date(s)
{
	\begin{cvitems} % Description(s) of tasks/responsibilities
		\item {Managed to increase the presence of the committee within the students' community.}
		\item {Increased the number of incoming feedback by up to 500\% by implementing proactive feedback gathering methods.}
		\item {Gathered opinions from the students regarding a possible amendment to the Charter of the Union.}
		\item {Organized an extraordinary council session addressing the amendment to the Charter.}
	\end{cvitems}
}

%---------------------------------------------------------
\cventry
{Council Secretary, Council of Supervisory and Representatives} % Job title
{} % Organization
{} % Location
{March 2018 - March 2019} % Date(s)
{
	\begin{cvitems} % Description(s) of tasks/responsibilities
		\item {Archived incoming letters and notices addressed to the council and wrote responses if necessary.}
		\item {Wrote and archived decision letters, documents, and notices of the council.}
		\item {Wrote and authorized the council's minutes of meetings.}
	\end{cvitems}
}

%---------------------------------------------------------
\cventry
{Member of Representatives, Council of Supervisory and Representatives} % Job title
{} % Organization
{} % Location
{Sept 2017 - March 2018} % Date(s)
{
	\begin{cvitems} % Description(s) of tasks/responsibilities
		\item {Approached fellow union members to ask for feedback and suggestions for the union.}
		\item {Proposed policies and solutions to the council and the executive body of the union based on suggestions and feedback from peers.}
	\end{cvitems}
}

%---------------------------------------------------------
\cventry
{Senior Technical Advisor} % Job title
{Dagozilla Robotics (Autonomous Vehicle Research Group Lab, ITB)} % Organization
{Bandung, Indonesia} % Location
{Sept 2019 - Sept 2020} % Date(s)
{
	\begin{cvitems} % Description(s) of tasks/responsibilities
		\item {Advised the team on nontechnical and technical subjects.}
		\item {Did more advanced research in state estimation.}
	\end{cvitems}
}

%---------------------------------------------------------
\cventry
{Lead Software Engineer} % Job title
{} % Organization
{} % Location
{Sept 2018 - Sept 2019} % Date(s)
{
	\begin{cvitems} % Description(s) of tasks/responsibilities
		\item {Led the design and development process of the software system for a telepresence robot as well as the documentation of the system.}
		\item {Directed the research and development on computer vision, robotic control systems, robot AI, and software UI/UX for MSL-class robots.}
		\item {Initiated better engineering and software documentation practices that enable the sharing of knowledge between divisions.}
	\end{cvitems}
}

%---------------------------------------------------------
\cventry
{Software Engineer} % Job title
{} % Organization
{} % Location
{Sept 2017 - Sept 2018} % Date(s)
{
	\begin{cvitems} % Description(s) of tasks/responsibilities
		\item {Designed and built the computer vision software component for MSL-class competition robots using OpenCV with ROS in C++.}
		\item {Created software documentation of the vision system that I built as well as other legacy codes that were going to be migrated.}
%		\item {Initiated the research on a pose estimation method by combining odometry and IMU sensor data using Extended Kalman Filter.}
	\end{cvitems}
}

\end{cventries}
