%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
	\cventry
	{A mobile telepresence robot that can be controlled remotely via the internet used for teleconference} % Degree
	{Mobile Telepresence Robot} % Institution
	{Robotics} % Location
	{2018--2019} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {The robot has been shown in various national exhibitions and technology-related conferences.}
			\item {Developed the robot software with Robot Operating System (ROS) and programmed the microcontroller (STM32).}
			\item {Created video chat software for the robot-mounted and user-facing applications using WebRTC.}
			\item {Used ROS, Python, C++, Node.js, socket.io, and WebRTC for this project.}
		\end{cvitems}
	}
    %---------------------------------------------------------
    
    \cventry
    {A team of mobile robots that compete in RoboCup Middle Size League} % Degree
    {Mobile Soccer Robot Development} % Institution
    {Robotics} % Location
    {2017--2020} % Date(s)
    {
    	\begin{cvitems} % Description(s) of tasks/responsibilities
    		\item {Developed the robot software with ROS and did simulations of the robots in match environments on Gazebo.}
    		\item {Applied software development practices in the development of the robot software.}
    		\item {Contributed to the design of the computer vision system and the AI for robots' behavior.}
    		\item {Used ROS, Gazebo, Python, C++, and Node.js for this project.}
    	\end{cvitems}
    }
    %---------------------------------------------------------
    
    \cventry
    {A simpler and plainer version of Google Docs} % Degree
    {Peer-to-Peer Collaborative Editor} % Institution
    {Distributed System} % Location
    {2019} % Date(s)
    {
    	\begin{cvitems} % Description(s) of tasks/responsibilities
    		\item {Created peer-to-peer collaborative text editor (simpler replica of Google Docs) utilizing CRDT.}
    		\item {Built the graphical user interface with Qt.}
    		\item {Used Python and C++ for the project.}
    	\end{cvitems}
    }
    %---------------------------------------------------------
    
    \cventry
    {Using pure image processing techniques without any learning algorithms to read license plates} % Degree
    {Vision-Based Vehicle License Plate Reader} % Institution
    {Image Processing} % Location
    {2019} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Built a custom image processing library for the recognition.}
            \item {Used pure image processing methods to recognize characters on license plates.}
            \item {Created a web-based graphical user interface for the application.}
            \item {Used C++, Javascript, and WebAssembly for this project.}
        \end{cvitems}
    }
    %---------------------------------------------------------
    
    \cventry
        {A system for West Java govt. to monitor and track the progress of current and planned programmes} % Degree
        {Programme Monitoring and Evaluation System} % Institution
        {Software} % Location
        {2019} % Date(s)
        {
            \begin{cvitems} % Description(s) of tasks/responsibilities
            	\item {Gathered functional and non-functional requirements from client (provincial government of West Java).}
                \item {Built the backend and frontend using PHP with Codeigniter framework.}
                \item {Used PHP for this project.}
            \end{cvitems}
        }
    %---------------------------------------------------------

%    \cventry
%        {An IoT prototype for smart home using Arduino, Raspberry Pi, and Android} % Degree
%        {Smart Home IoT Project} % Institution
%        {IoT System and Platforms} % Location
%        {2019} % Date(s)
%        {
%            \begin{cvitems} % Description(s) of tasks/responsibilities
%                \item {Created simple Android app to control lights and other home appliances via WiFi.}
%                \item {Implemented ROS nodes to communicate with hardware controllers.}
%            \end{cvitems}
%        }
    %---------------------------------------------------------
    
\end{cventries}
